Something about correlation functions

### 2021-07-02 paper-correlations.tex
Remove confusing TODO
Add some words about GPU

To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: \textbf{Insert nvidia gpu here}
\end{itemize}

@@

To measure efficiency of \code{Map} module we follow the same procedure but with
seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
cubes with a side $s = 50, 100, \dots, 350$ voxels.

The measurements of execution time is on \cref{fig:timings}.

\textbf{TODO: alogithmic efficiency for two and three dimensions as a function
  of number of elements.}

@@

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d.png}
    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
    \label{fig:timings-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d.png}
    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
    \label{fig:timings-3d}
  \end{subfigure}
    \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-map.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}}}
    \label{fig:timings-2d-map}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-map.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}}}
    \label{fig:timings-3d-map}
  \end{subfigure}
  \caption[]{\small Execution times for different correlation functions.}
  \label{fig:timings}
\end{figure*}
\twocolumngrid

>>>>

To measure efficiecy of our algorithms we use a machine with the following
configuration:
\begin{itemize}
\item \textbf{CPU}: AMD Ryzen 5 1600X running at 2200~MHz
\item \textbf{Memory}: 32~Gb DDR4-2400 memory
\item \textbf{GPU}: Nvidia GeForce GTX 1650 with 4~Gb video memory
\end{itemize}

@@

To measure efficiency of \code{Map} module we follow the same procedure but with
seven arrays usings squares with a side $s = 1000, 2000, \dots, 7000$ pixels and
cubes with a side $s = 50, 100, \dots, 350$ voxels. The surface-void correlation
functions on \cref{fig:timings-2d-gpu} and \cref{fig:timings-3d-gpu} are
calculates with a lesser number of sides because it's too demanding in video
memory.

Also many functions in \code{Map} module can utilize Nvidia's GPUs using the
CUDA library. For example, two-point correlation function uses FFT transform
optimized for Nvidia GPUs and provided in \code{CUDA.FFT} package. The choice
between CPU or GPU version is made depending on type of input array. If it's
\code{CuArray} rather than generic \code{AbstractArray} then CUDA implementation
is chosen.

The measurements of execution time is on \cref{fig:timings}. As you can see, GPU
versions (when available) are faster than CPU versions and limited only by
amount of video memory. Functions in \code{Directional} are slower (with
exception of the lineal-path function) but are also useful in media
reconstruction algorithms which utilize simulated annealing.

@@

\onecolumngrid
\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d.png}
    \caption[]{{\small Two-dimensional case, module \code{Directional}}}
    \label{fig:timings-2d}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d.png}
    \caption[]{{\small Three-dimensional case, module \code{Directional}}}
    \label{fig:timings-3d}
  \end{subfigure}
  \vskip\baselineskip
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-map.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}, CPU}}
    \label{fig:timings-2d-map}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-map.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}, CPU}}
    \label{fig:timings-3d-map}
  \end{subfigure}
  \vskip\baselineskip
    \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-2d-gpu.png}
    \caption[]{{\small Two-dimensional case, module \code{Map}, GPU}}
    \label{fig:timings-2d-gpu}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.475\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/time-3d-gpu.png}
    \caption[]{{\small Three-dimensional case, module \code{Map}, GPU}}
    \label{fig:timings-3d-gpu}
  \end{subfigure}
  \caption[]{\small Execution times for different correlation functions.}
  \label{fig:timings}
\end{figure*}
\twocolumngrid
